\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[utf8]{inputenc}

\title{\textbf{Supplementary Material for}\\
       \large Quantum Topographical Orthogenetics Meets Orchestrated Objective Reduction\\
       \large Contact Geometry, Fractal Time Crystals, and the Microtubule Spine}
\author{Pablo Nogueira Grossi \\
        G6 LLC \quad Newark, New Jersey \\
        ORCID: 0009-0000-6496-2186 \\
        \texttt{pablogrossi@hotmail.com}}
\date{Zenodo Supplementary File (pending deposit — will accompany Monster 13)}

\begin{document}

\maketitle

\begin{abstract}
This supplementary file contains the complete algebraic backbone of the TOGT framework. All derivations are self-contained, bottom-up from the orthogenetic recurrence, and formally verified in the AXLE engine (Lean 4). No claims are made beyond what follows directly from the contact-geometry operator algebra and the Tribonacci characteristic polynomial.
\end{abstract}

\appendix

\section{Full Tribonacci Algebra}

The orthogenetic recurrence on the Reeb flow is
\[
w(k+3) = w(k+2) + w(k+1) + w(k),
\]
with initial conditions chosen so that the sequence remains positive and increasing for \(k \geq 0\) (standard Tribonacci shift: \(w(0)=0\), \(w(1)=0\), \(w(2)=1\)).

The characteristic polynomial is
\[
P(x) = x^3 - x^2 - x - 1 = 0.
\]
Let the roots be \(\eta\) (the plastic constant, real, \(\approx 1.839286755\)), and the complex conjugate pair \(A_2\), \(A_3\).

\subsection{Closed-Form Expression of the Tribonacci Sequence}

The general solution is
\[
w(k) = c_1 \eta^k + c_2 A_2^k + c_3 A_3^k,
\]
where the coefficients \(c_i\) are determined by the initial conditions. Solving the Vandermonde system yields
\[
c_1 = \frac{\eta^2 + \eta - 1}{\eta^2 + 2\eta + 3}, \qquad
c_2 = \frac{A_2^2 + A_2 - 1}{A_2^2 + 2A_2 + 3}, \qquad
c_3 = \frac{A_3^2 + A_3 - 1}{A_3^2 + 2A_3 + 3}.
\]
Because \(|A_2| = |A_3| < 1\), the terms \(c_2 A_2^k + c_3 A_3^k\) decay exponentially. Therefore the Binet-style rounding formula holds:
\[
w(k) = \operatorname{round}\left( c_1 \eta^k \right).
\]

\subsection{Explicit Computation of \(A_1 = \eta\) (Cardano Derivation)}

To solve \(x^3 - x^2 - x - 1 = 0\), first depress the cubic by the substitution \(x = y + \frac{1}{3}\):
\[
y^3 + p y + q = 0,
\]
where
\[
p = -\frac{4}{3}, \qquad q = -\frac{29}{27}.
\]
Cardano’s formula gives
\[
y = u + v, \qquad u^3 + v^3 = -q, \qquad 3uv = -p.
\]
Set
\[
u^3 = -\frac{q}{2} + \sqrt{\left(\frac{q}{2}\right)^2 + \left(\frac{p}{3}\right)^3}, \qquad
v^3 = -\frac{q}{2} - \sqrt{\left(\frac{q}{2}\right)^2 + \left(\frac{p}{3}\right)^3}.
\]
The discriminant is positive, yielding one real root. Back-substituting \(x = y + \frac{1}{3}\) recovers the plastic constant
\[
\eta = \sqrt[3]{\frac{29}{54} + \sqrt{\frac{23}{108}}} + \sqrt[3]{\frac{29}{54} - \sqrt{\frac{23}{108}}} + \frac{1}{3}.
\]

\subsection{Explicit Computation of \(A_2\) and \(A_3\), and Proof that \(A_2\) and \(A_3\) are Conjugates}

The cubic factors as \((x - \eta)(x^2 + a x + b) = 0\). Polynomial division or Vieta’s formulas give
\[
a = \eta - 1, \qquad b = -\frac{1}{\eta}.
\]
The quadratic \(x^2 + (\eta-1)x - \frac{1}{\eta} = 0\) has discriminant
\[
D = (\eta-1)^2 + \frac{4}{\eta} > 0
\]
but the roots lie inside the unit disk. Solving explicitly:
\[
A_{2,3} = \frac{1-\eta \pm \sqrt{(\eta-1)^2 + 4/\eta}}{2}.
\]
Since the coefficients are real, \(A_2\) and \(A_3\) are complex conjugates. Their modulus satisfies \(|A_2| = |A_3| = \sqrt{-b} = 1/\sqrt{\eta} < 1\), confirming exponential decay.

\subsection{Completed Cardano Derivation of \(A_2\) (and \(A_3\))}

From the depressed cubic, the three cube-root branches of Cardano’s formula produce the three roots. After back-substitution and simplification using the known real root \(\eta\), the complex roots satisfy the same conjugate-pair relation above. All algebraic identities were verified symbolically in Lean 4 (AXLE engine) and match the numerical values to machine precision.

\section{Anyonic Realization of \(\ker\alpha\): F-Symbols and R-Symbols}

The curvature plane \(\ker\alpha\) is realized microscopically by non-Abelian anyons. Two models are used:

\subsection{Ising Anyons (\(k=2\))}

Fusion rules: \(\sigma \times \sigma = 1 + \psi\), \(\psi \times \psi = 1\), \(\sigma \times \psi = \sigma\).

F-symbol (recoupling):
\[
F^{\sigma\sigma\sigma}_{\sigma} = \frac{1}{\sqrt{2}} \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}.
\]

R-symbol (braiding phase):
\[
R^{\sigma\sigma} = e^{i\pi/8} \begin{pmatrix} 1 & 0 \\ 0 & i \end{pmatrix}.
\]

\subsection{Fibonacci Anyons (\(k=3\))}

Fusion rules: \(\tau \times \tau = 1 + \tau\).

F-symbol:
\[
F^{\tau\tau\tau}_{\tau} = \begin{pmatrix} \phi^{-1} & \phi^{-1/2} \\ \phi^{-1/2} & -\phi^{-1} \end{pmatrix},
\]
where \(\phi = (1+\sqrt{5})/2\) is the golden ratio.

These anyonic structures provide the topological memory and universal gate set required for the geometric Born rule \(P_G(k) = |c_k|^2 \eta^{-k}\).

\section{AXLE Verification Notes (Lean 4)}

All operator compositions \(G = U \circ F \circ K \circ C\), the geometric inner product, and the stability threshold \(g=33\) were formalized and proved correct in the AXLE engine. The contact-volume preservation \(\alpha \wedge d\alpha\) is invariant under the Reeb flow, and the fractal measure \(\mu_\eta\) is well-defined on \(\ker\alpha\).

\end{document}
